TBD

### 2021-02-19 outputs/paper/paper.Rmd
Statistical tests for Q5,-8, 10, 12, and 14
Chi-Square tests for Q7 onward, student t-tests for Q5-6.

Next step: re-order things and format them.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(wesanderson)
library(RColorBrewer)
library(ggthemes)
library(scales)

all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
#control_group <-
 # readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  #filter(type == "Control")
#treatment_group <-
 # readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  #filter(type == "Treated")
```

@@

kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))

```

```{r Q5 + Q6 Bar Graphs, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?

#ggplot(data = treatment_group, mapping = aes(x = Q5)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "# of employees prior to (date) for treatment group") +
  #theme_minimal()

#ggplot(data = control_group, mapping = aes(x = Q5)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "# of employees prior to (date) for control group",
     #   group = "Legend") +
  #theme_minimal()

#ggplot(data = treatment_group, mapping = aes(x = Q6)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "Current # of employees for treatment group") +
  #theme_minimal()

#ggplot(data = control_group, mapping = aes(x = Q6)) +
 #  geom_bar() +
  # labs(x = "# of employees",
   #     y = "# of restaurants",
    #    title = "Current # of employees for control gruop") +
  # theme_minimal()

```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(wesanderson)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)

all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
```

@@

kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
```

@@

## Statistical Tests

```{r statistical tests, echo = FALSE, message = FALSE}
### Welch's T-Test

# Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
tidy(t.test(control_q5, treatment_q5))

#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
tidy(t.test(control_q6, treatment_q6))

### Paired T-Test

tidy(t.test(all_simulated_dataset$Q5,
       all_simulated_dataset$Q6,
       paired=TRUE,
       conf.level = 0.95))

# Chi-Square

#Q7

q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type)
tidy(chisq.test((q7_chi)))

#Q8

q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type)
tidy(chisq.test((q8_chi)))

#Q10

q10_chi <- table(all_simulated_dataset$Q10, all_simulated_dataset$type)
tidy(chisq.test((q10_chi)))

#Q12

q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type)
tidy(chisq.test((q12_chi)))

#Q14

q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type)
tidy(chisq.test((q14_chi)))
```
